---
title: "Setup-Google-OAuth"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setup-Google-OAuth}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(gdrive.automation)
library(googledrive)
```

The main goal we want to do is authorize programmatic access to the google drive. When we use `googledrive` in an interactive session, it will prompt us to authorize access. Our steps therefore are:
1. authorize access
2. save the "token" that authenticates us for access
3. encrypt the token
4. save the decryption key as an environmental variable

Results:
* The encrypted token can then be shared without concern.
* The decryption key can live as a github secret that enables github actions to use the token for access

```{r create token}
# set up a local file cache for a new token
options(gargle_oauth_cache = ".secrets")
gargle::gargle_oauth_cache()

# create a new token
drive_auth(email = TRUE, scopes = "https://www.googleapis.com/auth/drive")
my_token <- drive_token()
```

```{r setup encryption key}
key <- gargle::secret_make_key()
cat(paste0("GDRIVE_KEY=", key)) # copy the result of this string
usethis::edit_r_environ() # run this to open your .Renviron file

# paste the result into that file
# restart your R session
```

```{r encrypt a new token and save it in inst/secrets/gs4-auth.token}
gargle::secret_write_rds(
    x = my_token, 
    path = ".secrets/gdrive-token.rds", 
    key = "GDRIVE_KEY"
)

# check that the token can be decrypted
stopifnot(!is.null(decrypt_gdrive_token()))
```
